A workflow for open source scientific articles

### 2022-01-14 src/tex/ms.tex
restructure
beauty

% Define document class
\documentclass[twocolumn]{aastex631}

@@

% Title
\title{\showyourwork: a workflow for open source scientific articles}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
        \caption{
            The effect of binary eccentricity on the detectability of a \emph{LISA} gravitational wave source; reproduced from Figure 3 in \citet{Wagg2021}. 
            This figure was automatically generated from the script \texttt{src/figures/eccentricity.py}.
        }
        \label{fig:eccentricity}
    \end{centering}
\end{figure}

\begin{figure}[th!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/banner.png}
        \caption{
            The default \texttt{README.md} banner in a repository instantiated from the \texttt{showyourwork-template}, with links to the \texttt{GitHub Action} build logs, a tarball containing the \texttt{TeX} source for the article, a directed acyclic graph (DAG) of the build process, and the compiled article PDF, respectively.
            Note that since this figure is a screenshot, we place it in the \texttt{src/static} folder and \texttt{git}-commit it.
            The workflow skips the generation step for any figures in that directory; note the absence of a margin icon next to this caption.
        }
        \label{fig:banner}
    \end{centering}
\end{figure}

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

@@

% Title
\title{A workflow for open source scientific articles}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/eccentricity.pdf}
        \caption{Foo}
        \label{fig:eccentricity}
    \end{centering}
\end{figure}

\begin{figure}[th!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/banner.png}
        \caption{FOO}
        \label{fig:banner}
    \end{centering}
\end{figure}
